### 2009-02-02 articles/2009/geoinformatics/article.tex
created images for the article and author information
git-svn-id: https://svn.osgeo.org/qgis/trunk@10092 c8812cc2-4d05-0410-92ff-de0c093fc19c

\begin{figure}[h]
   \begin{center}
   \caption{Quantum GIS 1.0.0 'Kore'}\label{fig:qgis10}\smallskip
   \includegraphics[clip=true, width=12cm]{qgis10}
\end{center}
\end{figure}

@@

\begin{figure}[h]
   \begin{center}
   \caption{QGIS Geoprocessing Tools}
    \label{fig:geoprocessing}\smallskip
   \includegraphics[clip=true, width=8cm]{geoprocessing}
\end{center}
\end{figure}

@@

\begin{figure}[h]
   \begin{center}
   \caption{One of the QGIS Core Plugin (GRASS GIS Integration)}
    \label{fig:grass-plugin}\smallskip
   \includegraphics[clip=true, width=14cm]{grass-plugin}
\end{center}
\end{figure}

@@

\begin{figure}[h]
   \begin{center}
   \caption{QGIS Python Plugin Installer}\label{fig:python-plugin}\smallskip
   \includegraphics[clip=true, width=14cm]{python-plugin-installer}
\end{center}
\end{figure}

@@

Otto Dassau <dassau@nature-consult.de>
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
South africa where he provides commercial support and development services for
QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich and for his company that provides programming and consulting services for FOSS GIS software.
\\Paolo Cavallini <cavallini@faunalia.it>

>>>>

\begin{figure}[h]
   \begin{center}
   \caption{Quantum GIS 1.0.0 'Kore'}\label{fig:qgis10}\smallskip
   \includegraphics[clip=true, width=10cm]{qgis10}
\end{center}
\end{figure}

@@

\begin{figure}[h]
   \begin{center}
   \caption{Shapefile to PostGIS Import Tool}
    \label{fig:spit}\smallskip
   \includegraphics[clip=true, width=10cm]{spit}
\end{center}
\end{figure}

@@

\begin{figure}[h]
   \begin{center}
   \caption{One of the QGIS Core Plugin (GRASS GIS Integration)}
    \label{fig:grass-plugin}\smallskip
   \includegraphics[clip=true, width=10cm]{grass-plugin}
\end{center}
\end{figure}

@@

\begin{figure}[h]
   \begin{center}
   \caption{QGIS Python Plugin Installer}\label{fig:python-plugin}\smallskip
   \includegraphics[clip=true, width=10cm]{python-plugin-installer}
\end{center}
\end{figure}

@@

Otto Dassau <dassau@nature-consult.de>: Otto lives in Hannover, Germany. His
background is Open Source GIS and applied remote sensing. 
\\Gary Sherman <sherman@mrcc.com>
\\Tim Sutton <tim@linfiniti.com>: Tim runs a consultancy business in Gauteng,
South africa where he provides commercial support and development services for
QGIS and other FOSS GIS software.
\\Marco Hugentobler <marco.hugentobler@karto.baug.ethz.ch>: Marco lives in Zurich, Switzerland. He works for the Institute of Cartography, ETH Zurich and for his company that provides programming and consulting services for FOSS GIS software.
\\Paolo Cavallini <cavallini@faunalia.it>
